---
title: "mlBioNets"
author:
- name: Víctor Lázaro-Vidal
  affiliation: Universidad Autónoma de Querétaro
- name: Valeria Hernández Zendejas
  affiliation: Universidad Autónoma de Querétaro
- name: Roberto Álvarez-Martínez
  affiliation: Universidad Autónoma de Querétaro
  email: roberto.alvarez@uaq.edu.mx
package: mlBioNets
output:
  BiocStyle::html_document
html_document:
  code_folding: show
abstract: |
  Description of your vignette
vignette: |
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Network inference

Load and preprocessing of data

```{r load_data, echo=TRUE}
# Load packages and data
library(mlBioNets)
library(phyloseq)
BN_bacter<-data(beetle_nightshade)
# Let's extract the taxonomic and abundance tables
T_table<-as.data.frame(tax_table(beetle_nightshade)); dim(T_table)

O_table<-as.data.frame(t(otu_table(beetle_nightshade))); dim(O_table)

# The ASVs abundances are collapsed at genus level
BN_bacter2<-T_collapse(is_phyloseq = F, T_table = T_table,
                       O_table = O_table,
                       names_level = "Genus"); dim(BN_bacter2)

# Eliminate unclassified data
BN_bacter2<-BN_bacter2[,-c(which(colnames(BN_bacter2)=="unclassified"))]

# Separate beetle and nightshade samples' ID
Insect<-which(phyloseq::sample_data(beetle_nightshade)$Type =="Insect")
Insect<-phyloseq::sample_data(beetle_nightshade)$ID[Insect]; Insect

Plant<-which(sample_data(beetle_nightshade)$Type =="Plant")
Plant<-sample_data(beetle_nightshade)$ID[Plant]; Plant

# Separate abundances
Insectmat <- BN_bacter2[Insect,]
Plantmat <- BN_bacter2[Plant,]
```

# Network inference using the SparCC algorithm

```{r NetInf_SparCC, echo=TRUE, results='hide'}
library(igraph)
# Beetle layer
library(SpiecEasi)
sparccNet<-sparcc(Insectmat)
sparccNet <- abs(sparccNet$Cor) >= 0.4
insect_sparCC<-adj2igraph(sparccNet)
vertex.attributes(insect_sparCC) <- list(name = colnames(Insectmat))
plot_network(insect_sparCC)
# Nightshade layer
sparccNet<-sparcc(Plantmat)
sparccNet <- abs(sparccNet$Cor) >= 0.4
plant_sparCC<-adj2igraph(sparccNet)
vertex.attributes(plant_sparCC) <- list(name = colnames(Plantmat))
plot_network(plant_sparCC)
```

## Multilayer plotting

```{r MultilayerPlt1, echo=TRUE, warning=FALSE, message=FALSE}
library(muxViz)
library(viridis)
library(rgl)
# Multilayer object
g.list<-list(insect_sparCC, plant_sparCC)
# Nodes' colors
g.list<-v_colored_ml(g.list, T_table, "Phylum", "Genus",
                     sample(viridis(100), length(unique(T_table[, "Phylum"]))))
matctr<-node_color_mat(g.list, "phylo")
# Nodes' size
matsize<-abs_mat(list(Insectmat, Plantmat), g.list, 10)
# Multilayer plot
lay <- layoutMultiplex(g.list, layout="kk", ggplot.format=F, box=T)
plot_multiplex3D(g.list, layer.layout=lay,
                 layer.colors=c("red3", "green3"),
                 layer.shift.x=0.5, layer.space=2,
                 layer.labels=NULL,
                 layer.labels.cex=1.5, node.size.values="auto",
                 node.size.scale=matsize,
                 node.colors=matctr,
                 edge.colors="black",
                 node.colors.aggr=NULL,
                 show.aggregate=F)
rglwidget()

```

# Network inference using ARACNe algorithm

```{r NetInf_ARACNe, echo=TRUE, warning=FALSE, message=FALSE}
library(minet)
# Beetle layer
mim <- build.mim(Insectmat,estimator="spearman")
Imat <- aracne(mim)
insect_aracne<-graph.adjacency(Imat)
insect_aracne<-as.undirected(insect_aracne)
plot_network(insect_aracne)
# Nightshade layer
mim <- build.mim(Plantmat,estimator="spearman")
Pmat <- aracne(mim)
plant_aracne<-graph.adjacency(Pmat)
plant_aracne<-as.undirected(plant_aracne)
plot_network(plant_aracne)
```

## Multilayer plotting

```{r MultilayerPlt2, echo=TRUE, warning=FALSE, message=FALSE}
library(muxViz)
library(viridis)
# Multilayer object
g.list<-list(insect_aracne, plant_aracne)
# Nodes' colors
g.list<-v_colored_ml(g.list, T_table, "Phylum", "Genus",
                     sample(viridis(100), length(unique(T_table[, "Phylum"]))))
matctr<-node_color_mat(g.list, "phylo")
# Nodes' size
matsize<-abs_mat(list(Insectmat, Plantmat), g.list, 10)
# Multilayer plot
lay <- layoutMultiplex(g.list, layout="kk", ggplot.format=F, box=T)
clear3d(type = "all")
plot_multiplex3D(g.list, layer.layout=lay,
                 layer.colors=c("red3", "green3"),
                 layer.shift.x=0.5, layer.space=2,
                 layer.labels=NULL,
                 layer.labels.cex=1.5, node.size.values="auto",
                 node.size.scale=matsize,
                 node.colors=matctr,
                 edge.colors="black",
                 node.colors.aggr=NULL,
                 show.aggregate=F)
rglwidget()


```

# Cross-references

Apart from referencing figures (Section \@ref(figures)), tables (Section \@ref(tables)), and equations (Section \@ref(equations)), you can also use the same syntax to refer to sections by their default labels generated by pandoc.

# Side notes

Footnotes are displayed as side notes on the right margin[^1], which has the advantage that they appear close to the place where they are defined.

[^1]: this is a side note entered as a footnote

# References {.unnumbered}

# Session info

```{r sessionInfo, echo=TRUE}
sessionInfo()
```
