---
title: "mlBioNets"
author:
- name: Víctor Lázaro-Vidal
  affiliation: Universidad Autónoma de Querétaro
- name: Valeria Hernández Zendejas
  affiliation: Universidad Autónoma de Querétaro
- name: Roberto Álvarez-Martínez
  affiliation: Universidad Autónoma de Querétaro
  email: roberto.alvarez@uaq.edu.mx
package: mlBioNets
output:
  BiocStyle::html_document
abstract: |
  Description of your vignette
vignette: |
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Network inference

Load and preprocessing of data

```{r small, fig.cap="Small figure. A plot produced by a code chunk with option `fig.small = TRUE`.", fig.small=TRUE, echo=FALSE}
# Load packages and data
library(mlBioNets)
library(phyloseq)
BN_bacter<-data(ps2)
# Let's extract the taxonomic and abundance tables
T_table<-as.data.frame(tax_table(ps2)); dim(T_table)
O_table<-as.data.frame(t(otu_table(ps2))); dim(O_table)
# The ASVs abundances are collapsed at genus level
BN_bacter2<-T_collapse(is_phyloseq = F, T_table = T_table,
                       O_table = O_table,
                       names_level = "Genus"); dim(BN_bacter2)
# Eliminate unclassified data
BN_bacter2<-BN_bacter2[,-c(which(colnames(BN_bacter2)=="unclassified"))]
# Separate beetle and nightshade samples' ID
Insect<-which(sample_data(ps2)$Type =="Insect")
Insect<-sample_data(ps2)$ID[Insect]; Insect
Plant<-which(sample_data(ps2)$Type =="Plant")
Plant<-sample_data(ps2)$ID[Plant]; Plant
# Separate abundances
Insectmat <- T_Collapsed[Insect,]
Plantmat <- T_Collapsed[Plant,]
```

Network inference using the SparCC algorithm

```{r}
library(igraph)
# Beetle layer
library(SpiecEasi)
sparccNet<-sparcc(Insectmat)
sparccNet <- abs(sparccNet$Cor) >= 0.4
insect_sparCC<-adj2igraph(sparccNet)
vertex.attributes(insect_sparCC) <- list(name = colnames(Insectmat))
plot_network(insect_sparCC)
# Nightshade layer
sparccNet<-sparcc(Plantmat)
sparccNet <- abs(sparccNet$Cor) >= 0.4
plant_sparCC<-adj2igraph(sparccNet)
vertex.attributes(plant_sparCC) <- list(name = colnames(Plantmat))
plot_network(plant_sparCC)
```

Multilayer plotting

```{r}
library(muxViz)
library(viridis)
# Multilayer object
g.list<-list(insect_sparCC, plant_sparCC)
# Nodes' colors
g.list<-v_colored_ml(g.list, T_table, "Phylum", "Genus",
                     sample(viridis(100), length(unique(T_table[, "Phylum"]))))
matctr<-node_color_mat(g.list, "phylo")
# Nodes' size
matsize<-abs_mat(list(Insectmat, Plantmat), g.list, 10)
# Multilayer plot
lay <- layoutMultiplex(g.list, layout="kk", ggplot.format=F, box=T)
plot_multiplex3D(g.list, layer.layout=lay,
                 layer.colors=c("red3", "green3"),
                 layer.shift.x=0.5, layer.space=2,
                 layer.labels=NULL,
                 layer.labels.cex=1.5, node.size.values="auto",
                 node.size.scale=matsize,
                 node.colors=matctr,
                 edge.colors="black",
                 node.colors.aggr=NULL,
                 show.aggregate=F)

```

Network inference using ARACNe algorithm

```{r}
library(minet)
# Beetle layer
mim <- build.mim(Insectmat,estimator="spearman")
Imat <- aracne(mim)
insect_aracne<-graph.adjacency(Imat)
insect_aracne<-as.undirected(insect_aracne)
plot_network(insect_aracne)
# Nightshade layer
mim <- build.mim(Plantmat,estimator="spearman")
Pmat <- aracne(mim)
plant_aracne<-graph.adjacency(Pmat)
plant_aracne<-as.undirected(plant_aracne)
plot_network(plant_aracne)
```

Multilayer plotting

```{r}
library(muxViz)
library(viridis)
# Multilayer object
g.list<-list(insect_aracne, plant_aracne)
# Nodes' colors
g.list<-v_colored_ml(g.list, T_table, "Phylum", "Genus",
                     sample(viridis(100), length(unique(T_table[, "Phylum"]))))
matctr<-node_color_mat(g.list, "phylo")
# Nodes' size
matsize<-abs_mat(list(Insectmat, Plantmat), g.list, 10)
# Multilayer plot
lay <- layoutMultiplex(g.list, layout="kk", ggplot.format=F, box=T)
plot_multiplex3D(g.list, layer.layout=lay,
                 layer.colors=c("red3", "green3"),
                 layer.shift.x=0.5, layer.space=2,
                 layer.labels=NULL,
                 layer.labels.cex=1.5, node.size.values="auto",
                 node.size.scale=matsize,
                 node.colors=matctr,
                 edge.colors="black",
                 node.colors.aggr=NULL,
                 show.aggregate=F)

```

# Getting started

To enable the *Bioconductor* style in your R Markdown vignette you need to include the following in the `DESCRIPTION` file:

```         
VignetteBuilder: knitr
Suggests: BiocStyle, knitr, rmarkdown
```

# Style macros

*BiocStyle* introduces the following macros for referring to *R* packages:

-   `r Biocpkg("IRanges")`, for *Bioconductor* software, annotation and experiment data packages,
-   `r CRANpkg("data.table")`, for *R* packages available on CRAN,
-   `r Githubpkg("rstudio/rmarkdown")`, for *R* packages available on GitHub,
-   `r Rpackage("MyPkg")`, for *R* packages that are *not* available on *Bioconductor*, CRAN or GitHub.

# Figures

Assign captions to figures in the code chunk option `fig.cap` to automatically number them, and to be able to reference them, see Figure \@ref(fig:plot). The figure label is generated from the code chunk label by prefixing it with `fig:`.

```{r plot, fig.cap="Regular figure. The first sentence of the figure caption is automatically emphasized to serve as figure title.", echo=FALSE}
plot(cars)
```

Small and wide figures can be specified by `fig.small` and `fig.wide` code chunk options.

```{r small, fig.cap="Small figure. A plot produced by a code chunk with option `fig.small = TRUE`.", fig.small=TRUE, echo=FALSE}
plot(cars)
```

```{r wide, fig.cap="Wide figure. A plot produced by a code chunk with option `fig.wide = TRUE`.", fig.wide=TRUE, echo=FALSE}
plot(cars)
```

# Equations

To number and reference equations, put them in equation environments and assign labels to them, see Equation \@ref(eq:binom).

\begin{equation}
  f\left(k\right) = \binom{n}{k} p^k\left(1-p\right)^{n-k}
  (\#eq:binom)
\end{equation}

# Tables

Like figures, tables with captions will also be numbered and can be referenced, see Table \@ref(tab:table).

| Fruit   | Price |
|---------|-------|
| bananas | 1.2   |
| apples  | 1.0   |
| oranges | 2.5   |

: (#tab:table) A simple table. With caption.

# Cross-references

Apart from referencing figures (Section \@ref(figures)), tables (Section \@ref(tables)), and equations (Section \@ref(equations)), you can also use the same syntax to refer to sections by their default labels generated by pandoc.

# Side notes

Footnotes are displayed as side notes on the right margin[^1], which has the advantage that they appear close to the place where they are defined.

[^1]: this is a side note entered as a footnote

# References {.unnumbered}

# Session info

```{r sessionInfo, echo=FALSE}
sessionInfo()
```
